\documentclass[a4paper]{deedy-resume} % Use A4 paper
\usepackage{enumitem}
\usepackage{multicol}
\setlist[itemize]{topsep=-2pt,itemsep=0pt,partopsep=4pt,parsep=4pt} % Tighter spacing for compactness
\setlist[description]{topsep=0pt,itemsep=2pt,partopsep=4pt,parsep=4pt}

% Define custom colors for headings and rules

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Karishma}{Arun Bodupali}{
    \vspace{-5pt}
    \urlstyle{same}\url{karibodu2708@gmail.com} \hspace{0.5cm} \urlstyle{same}\url{linkedin.com/in/karishma-bodupali}
    \begin{center}
        \runsubsection{Strategic regulatory project manager with 4+ years of experience in global submissions, product lifecycle strategy, 
        and AI-driven process enhancements. Skilled in cross-functional leadership and stakeholder management, optimizing compliance with EMA, FDA, and
         MHRA regulations while delivering measurable business impact and up to 40\% efficiency gains.}
    \end{center}
    \vspace{-10pt}
}
%----------------------------------------------------------------------------------------
% Work Experience
%----------------------------------------------------------------------------------------

\vspace{-10pt}
\section{Work Experience}

\runsubsection{\textbf{Novo Nordisk A/S}}
\descript{| \textbf{Project Manager \& Regulatory Professional}}
\begin{center}
    \vspace{-17pt}
    \rule{0.98\linewidth}{0.5pt}
    \vspace{-11pt}
\end{center}
    \runsubsubsection{\textbf{Regulatory Professional, Semaglutide}}
    \location{\textbf{(Aug 2024 – Present, Copenhagen, Denmark)}}
    \vspace{-10pt}
    \begin{multicols}{2}
        \begin{itemize}
            \item \textbf{Led} the rollout plan for new drug product submissions in \textbf{top 10 markets}, reducing preparation time by \textbf{30\%} through cross-functional collaboration.
            \item \textbf{Managed} regulatory submissions for Australia, Switzerland, and LATAM, ensuring adherence to international standards and timelines.
            \item \textbf{Acted} as the lead regulatory representative on cross-functional teams to ensure compliance for new product launches.
        \end{itemize}
    \end{multicols}    
\vspace{-10pt}
    \runsubsubsection{\textbf{Project Manager, RQ\&C Executive Office}}
    \location{\textbf{(Jun 2024 – Jul 2024, Copenhagen, Denmark)}}
    \vspace{-10pt}
    \begin{multicols}{2}
        \begin{itemize}
            \item \textbf{Directed} the global rollout of an AI-driven translation project across \textbf{4 regions}, coordinating over 10 stakeholders, resulting in streamlined processes and regional compliance.
            \item \textbf{Developed} a strategy based on historical translation error rates, enhancing translation efficiency by \textbf{25\%}.
            \item \textbf{Optimized} regional processes through end-user feedback, reducing rollout time by \textbf{15\%}.
        \end{itemize}
    \end{multicols}
\vspace{-10pt}
\runsubsubsection{\textbf{Regulatory Affairs Professional}}
\location{\textbf{(Sept 2022 – Dec 2023, London, U.K. \& Copenhagen, Denmark)}}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{Developed} the UK's first AI chatbot for regulatory inquiries, cutting response times by \textbf{40\%} and expanding access by \textbf{35\%}.
        \item \textbf{Achieved} 100\% SOP audit compliance in two months by revamping internal quality controls.
        \item \textbf{Devised} EMA and FDA submission strategies for complex digital health regulations.
    \end{itemize}
    \columnbreak
    \begin{itemize}
        \item \textbf{Submitted} SaMD dossiers to TÜV SÜD and FDA, accelerating market entry by \textbf{25\%}.
        \item \textbf{Implemented} Vault RIM, improving compliance to \textbf{99\%} and reducing document retrieval times by \textbf{30\%}.
    \end{itemize}
\end{multicols}

\vspace{-10pt}

\runsubsection{\textbf{Cartherics Pty Ltd}}
\runsubsubsection{| \textbf{Student Consultant}}
\location{\textbf{(Apr 2021 – Nov 2021, Melbourne, Australia)}}
\begin{center}
    \vspace{-17pt}
    \rule{0.98\linewidth}{0.5pt}
    \vspace{-11pt}
\end{center}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{Identified} 44 competitors using key data sources, leading to a \textbf{strategic shortlist of the top 10} presented to executive leadership.
        \item \textbf{Developed} a predictive model analysing competitors' clinical trials and manufacturing methods, guiding sales strategy.
        \item \textbf{Recommended} an expanded sales strategy based on model insights, adopted by senior executives to target additional indications.
    \end{itemize}
\end{multicols}
\vspace{-5pt}

\runsubsection{\textbf{Rakuten Mobile Inc}}
\runsubsubsection{| \textbf{Project Management Intern}}
\location{\textbf{(Oct 2019 – Jan 2020, Tokyo, Japan)}}
\begin{center}
    \vspace{-17pt}
    \rule{0.98\linewidth}{0.5pt}
    \vspace{-11pt}
\end{center}

\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item \textbf{Collaborated} with senior managers to translate technical details into actionable project goals and timelines.
        \item \textbf{Led} the deployment and testing of devices for \textbf{600+ users}, identifying \textbf{4\%} of network issues pre-4G launch in Japan.
        \item \textbf{Created and delivered} training for \textbf{300+ graduates} for a network testing event, enhancing project readiness and data collection.
    \end{itemize}
\end{multicols}

%----------------------------------------------------------------------------------------
% Education
%----------------------------------------------------------------------------------------

\vspace{-10pt}
\section{Education}
\vspace{-10pt}
\begin{multicols}{2}
    \begin{itemize}
        \item \runsubsection{\textbf{University of Melbourne}}
        \descript{| \textbf{MSc in Biotechnology (First Class Honors)}}
        \location{\textbf{(Mar 2020 – Dec 2021 | Melbourne, Australia)}}
        \columnbreak
        \item \runsubsection{\textbf{University of Tsukuba}}
        \descript{| \textbf{BSc in Biological Sciences}}
        \location{\textbf{(Sept 2015 – Aug 2019 | Tsukuba, Japan)}}
        \vspace{-2pt}
        \begin{itemize}
            \item Thesis: \textit{"Molecular Analysis of the KLHL7 Protein"}
        \end{itemize}
    \end{itemize}
\end{multicols}
\vspace{-5pt}
%----------------------------------------------------------------------------------------
% Technical Skills & Languages
%----------------------------------------------------------------------------------------

\vspace{-25pt}
\section{Technical Skills \& Languages}
\vspace{-10pt}
\begin{multicols}{2}
\runsubsection{\textbf{Technical Skills}} \\
MS Office \textbullet{} IBM SPSS \textbullet{} MS Project \textbullet{} Azure DevOps \textbullet{} Confluence \textbullet{} SharePoint \textbullet{} Power BI \textbullet{} Vault RIM
\columnbreak
\\ \runsubsection{\textbf{Languages}} \\
English (Fluent) \textbullet{} Hindi (Fluent) \textbullet{} Gujarati (Fluent) \textbullet{} Japanese (Intermediate)
\end{multicols}

\end{document}
