\documentclass[a4paper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
\usepackage{enumitem}
\setlist[itemize]{topsep=-2pt,itemsep=-1pt,partopsep=4pt,parsep=4pt}
\setlist[description]{topsep=0pt,itemsep=2pt,partopsep=4pt,parsep=4pt}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\namesection{Shashwat}{Dalal}{ % Your name
\begin{center}
    \runsubsection{   
    \hspace{2.25cm}Senior Machine Learning Engineer, Quantumblack
    \newline 
    Computing MEng, Imperial College London} 
\end{center}
\urlstyle{same}\url{shashdalal@gmail.com}
\hspace{0.5cm}
\urlstyle{same}\url{www.linkedin.com/in/shashwat-dalal}
\hspace{0.5cm}
\urlstyle{same}\url{shashwatdalal.github.io}
}
%------------------------------------------------
% Work Experience
%------------------------------------------------
\section{Work Experience}
\runsubsection{QuantumBlack (A McKinsey Company)}
\descript{| Junnior Principal Machine Learning Engineer }
\location{September 2020 – Current | London, United Kingdom}
\begin{itemize}
    \item \textbf{Tech Lead for Simulation-Based Optimization Group}: Guided and shaped 10+ client engagements across various industries, 
    including \textbf{energy, engineering, logistics, and life-science}, to optimize operations and improve decision-making processes through simulation and advanced analytics.
    \item \textbf{Bidding Agent for Battery Energy Storage System}: Led a team of 5 engineers to develop a \textbf{reinforcement learning} based bidding agent that 
    increased revenue by 34\% compared to a linear programming benchmark. Responsible for technical deliverables, project management, and system architecture.
    \item \textbf{Scaling Protein Engineering}: Led a migration of a protein engineering asset to an elastic GPU cluster using Ray and Kubernetes, significantly reducing costs 
    and boosting throughput for our life-science clients. For the protein folding pipeline, achieved a 57x speedup, a 70\% improvement in GPU utilization, 
    and a 30\% reduction in costs by scaling across a 20 V100 GPU cluster. For the molecular embedding pipeline, delivered a ~37x speedup, a 40x increase in throughput, 
    and a 60\% cost reduction.
    \item \textbf{Turbine Design Optimization}: Led the development of a distributed black-box optimizer for turbine operations and condition monitoring, 
    improving turbine efficiency by +0.4\% (validated by CFD) in 1/20th the time and at half the cost compared to previous methods. 
    The optimizer utilized genetic and Bayesian methods and ran on a GPU cluster of 20 machines using Ray.
    \item \textbf{Supply Chain Optimisation} Led a team of 6 in designing a linear optimization model for a global computer manufacturer, 
    aimed at unifying production and capacity planning across regions. Integrated with internal data platforms to enable API-driven decision-making 
    based on dynamic forecasts, backlog management, and third-party manufacturing capacity constraints.
    \item \textbf{Clinical Trial Optimization}: Spearheaded the data engineering workstream for optimizing clinical trial site selection. 
    Developed a unified training and inference data-engineering framework, which reduced project timelines by one week.
\end{itemize} 
\runsubsection{Bloomberg}
\descript{| Software Engineering Industrial Placement}
\location{April 2019 – September 2019 | London, United Kingdom}
\begin{description}
    \begin{itemize}
        \item Maintained \textbf{BuildStream}, an open source build and integration tool written in \textbf{Python}.
        \item Wrote a plugin to automate the creation of reproducible and layered \textbf{Docker} images.
        \\
        \textit{Report:} https://shashwatdalal.github.io/files/placement\_report.pdf \\
    \end{itemize}
\end{description}
\runsubsection{Barclays Investment Bank}
\descript{| Summer Technology Analyst}
\location{June 2018 – September 2018 | London, United Kingdom}
%------------------------------------------------
% Education
%------------------------------------------------
\section{Education}
    \runsubsection{Imperial College London}
    \descript{| Computing MEng. (Graduated 1st Class)}
    \location{2016 - 2020 | London, United Kingdom}
    \begin{description}
        \item[Academic Projects] \hspace{7.5cm}
            \begin{itemize}
                \item \textbf{Effect of Non-Identically Distributed Data on Federated Learning for Next-Word Prediction:} Final year project. \\
                \textit{Report: } https://shashwatdalal.github.io/files/fl\_fyp.pdf \\
                \textit{Slides: } https://bit.ly/3bpAU8g
                \item \textbf{Aspect-based Sentiment Analysis with Goldman Sachs:} In a team of six, built an aspect-based sentiment analysis engine for the asset management engineering team. Back-end written in \textbf{Python} and database layer used \textbf{MySQL}, and \textbf{Microsoft Cosmos}. \\
                \textit{Report:} https://shashwatdalal.github.io/files/Software\_Engineering\_Project\_Report.pdf \\ \textit{Code:} https://dev.azure.com/vapesoc/362\%20Software\%20Engineering\%20Project/
        \end{itemize}
    \end{description}
%------------------------------------------------
% Skill-Set Summarized
%------------------------------------------------
\section{Skill-Set Summarized}

\begin{minipage}[t]{0.45\textwidth}

\subsection{Technical Skills}
Java \textbullet{} Python \textbullet{} Docker \textbullet{} Kubernetes \textbullet{} Ray \textbullet{} PyTorch  \\  Deep Learning \textbullet{} Bayesian Optimisation \textbullet{} Reinforcement Learning \textbullet{} Federated Learning

\end{minipage}
\begin{minipage}[t]{10\textwidth}
\end{minipage}
\begin{minipage}[t]{0.45\textwidth}
\subsection{Languages}
English (Written/Spoken Fluency) \textbullet{} Gujarati (Spoken Fluency) \textbullet{} Japanese (Written/Spoken Conversational) \textbullet{} \\  Spanish (Written/Spoken Conversational)  \textbullet{} \\  Hindi (Spoken Conversational)

\end{minipage}

\end{document} 
